Stylistic Context Clustering for Token-Level Author Diarization

### 2017-07-06 paper/paper.tex
Fixed error.

Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$. A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label. For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
\begin{equation}
	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
\end{equation}
The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.

Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$. The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e., makes good predictions given unseen documents.

>>>>

Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$. A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label. For a segmentation to be valid, the segments must cover all terms in the document and not overlap.

The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$. Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$. The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e., makes good predictions given unseen documents.
